TODO title

### 2017-01-12 doc/paper/paper.tex
Drafting methods section.

\usepackage{cogsci}
\usepackage{pslatex}
\usepackage{apacite}

@@

\subsection{The Neural Engineering Framework}

\subsection{Leaky, competing accumulator model}

\subsection{Independent accumulator model}

* ever increasing evidence

>>>>

\usepackage{cogsci}
\usepackage{commath}
\usepackage{pslatex}
\usepackage{apacite}

@@

\subsection{The Neural Engineering Framework}
We employ the Neural Engineering Framework (NEF, TODO cite) which allows us to 
implement mathematical model descriptions in spiking neural networks based on 
three principles: \emph{representation}, \emph{transformation}, and 
\emph{dynamics}.

\subsubsection{Principle 1: Representation}
The representation of a value $x(t)$ with a population of spiking neurons is 
defined by the encoding and decoding. The encoding converting the value $x$ into 
a spike train or instantaneous firing rate $a_i(t)$ for neuron $i$ is given by
\begin{equation}
    a_i(t) = G_i\left[\alpha_i x(t) + J_i^{\mathrm{bias}}\right]
\end{equation}
where $\alpha_i$ is a gain factor, $J_i^{mathrm{bias}}$ a bias current and $G_i$ 
is the neuron linearity. Here, we use spiking leaky integrate-and-fire neurons 
for $G_i$.

Decoding weights $d_i$ are used to decode a value $\hat x(t)$ from such 
a population of neurons with
\begin{equation}
    \hat x(t) = \sum_i d_i \left[a_i(t) * h(t)\right]
\end{equation}
where $h(t) = \tau^{-1}\exp(1/\tau)$ is the synaptic filter. The decoding 
weights are obtained with a least-squares optimization of the error $E^x 
= \abs{x - \hat x}$.

For the transmission of a value from one population to another, the connection 
weights are given by
\begin{equation}
    W_{ij} = \alpha_j d_i \text{.}
\end{equation}

\subsubsection{Principle 2: Transformation}
By finding alternate decoding weights $d^f_i$ with the error given by $E^{f(x)} 
= \abs{f(x) - \hat x}$ arbitrary linear and non-linear functions $f(x)$ can be 
approximated in the connections between neural populations.

\subsubsection{Principle 3: Dynamics}
TODO

\subsection{Leaky, competing accumulator model}
We implement the widely used, leaky, competing accumulator model proposed by 
TODO\@. The dynamics for the state variables $x_i, i < N$, where $N$ is the 
number of choices, are given by
\begin{equation}\label{eqn:usher-mcclelland}
    \begin{split}
    dx_i &= \left(\rho_i - kx_i - \beta \sum_{j \neq i} x_j\right) 
    \frac{dt}{\tau'} \\
    x_i &\rightarrow \max(x_i, 0)
    \end{split}
\end{equation}
where $\rho_i$ is the external input, $k$ is the leak rate, $\beta$ the lateral 
inhibition, and $tau'$ the time constant. Note that one usually wants to set $k 
= \beta$ because TODO\@. Here, we chose $k = \beta = 1$. TODO what does changing 
this control? Why can we fix it at 1?

Equation~\ref{eqn:usher-mcclelland} can easily be implemented with the NEF by 
using one population of neurons for each $x_i$.  We believe this implementation 
to be novel as it it does not treat the $x_i$ as neural firing rates, rather the 
neural firing rates are weighted by the decoding weights to precisely implement 
the stated dynamics. As such the model equations do not impose restrictions on 
the neuron model or requires to lump the neurons into a single population firing 
rate. This allows us to use biologically more realistic neurons while at the 
same time adhering to the dynamics prescribed by the model.

TODO figure with dynamics

\subsection{Independent accumulator model}
The other Winner-take-all mechanism is related to the Usher-McClelland model and 
even more closely to independent accumulator models (TODO refs), but has some 
fine and important distinctions. It consists of two layers of neural 
populations. The first layer are independent accumulators obtained from 
Equation~\ref{eqn:usher-mcclelland} by setting $k = \beta = 0$ resulting in
\begin{equation}
    \begin{split}
    dx^1_i &= \lambda \rho_i \frac{dt}{\tau} \\
    x^1_i &\rightarrow \max(x^1_i, 0) \text{.}
    \end{split}
\end{equation}
The parameter $\lambda$ scales this input and is introduced because it is more 
convenient to manipulate than then the threshold parameter $\vartheta$ 
introduced below.

The second layer consists of independent non-recurrent populations that get 
input from the first layer in a one to one projection. We decode the shifted 
Heaviside function $\Theta(x^2_i - \vartheta)$ from it where $\vartheta = 0.8$ 
is a threshold value controlling how much evidence needs to be accumulated to 
produce an output. Instead of controlling this threshold, it is more convenient 
to scale the input with $\lambda$ in the context of the NEF, though 
mathematically both approaches are equivalent. As the Usher-McClelland does not 
have a threshold parameter, we do not introduce the input scaling $\lambda$ in 
that model.

The Heaviside decoded output of layer 2 projects back to layer 1 to add $x^2_i 
- 2\sum_{j \neq i} x^2_j$ to the input of $x^1_i$. As effect the choice will be 
stabilized while all other state variables will be suppressed once one of the 
accumulators reaches the threshold $\vartheta$.

TODO figure with dynamics

\section{Results}

\section{Discussion}
* ever increasing evidence
